\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{classic}                
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\firstname{Nicolas}
\familyname{Morey-Chaisemartin}
\title{Embedded Software Architect - Front-End and Operating System Developper}
\address{8 Rue Tristan Corbière}{38400 Saint Martin d'Hères}    
\mobile{+33 6 78 31 51 62}                    
\email{nicolas@morey-chaisemartin.com}                      
\homepage{www.nicolas.morey-chaisemartin.com}
\extrainfo{29/06/1986}

\begin{document}
\maketitle
\section{Work Experience}
\cventry{July 2009\\upto Today}{Embedded software architect and developper}{Kalray}{Montbonnot}{}
{
\begin{itemize}
\item[-]{Development of an embedded operating system and runtime library.}
\item[-]{Development of a front-end \textbf{compiler} for a highly parallel streaming language.}
\item[-]{In charge of \textbf{continuous integration} using Git/Hudson.}
\item[-]{IT Co-administrator .}
\item[-]{Environment: \textbf{Embedded systems}, MPPA, C, Assembly, Ruby, Parallel programming.}
\end{itemize}
}

\cventry{Octobre 2008\\upto July 2009}{Embedded System Engineer}{Coframi}{Meylan}{}
{
\begin{itemize}
\item[-]{Consulting for Bull in the R\&D HPC Team: \textbf{Infiniband} expert.}
\item[-]{Development of fault-tolerant \textbf{routing algorithms} (patents pending).}
\item[-]{Development of network monitoring solutions for large clusters..}
\item[-]{Environment: Infiniband, Routage, QoS, \textbf{Linux drivers}, \textbf{HPC}.}
\end{itemize}
}

\cventry{May 2008\\upto Septembre 2008}{MSc Project}{Northumbria University}{Newcastle}{UK}
{
\begin{itemize}
\item[-]{Design and development of a \textbf{hard real-time micro-Kernel} for the Cell Broadband Engine.}
\item[-]{Environment: \textbf{Multicore}, Real-Time, \textbf{Scheduling}, Synchronisation, C, Assembly.}
\end{itemize}
}

\cventry{June 2007\\upto August 2007}{IT Intern}{Allibert-Trekking}{Montmélian}{}
{
\begin{itemize}
\item[-]{User and server support on a Mac OS X infrastructure.}
\item[-]{Deployment of \textbf{monitoring tools}.}
\item[-]{Development of synchronisation tools between inventory, administration and monitoring tools.}
\item[-]{Environment: Mac OS X, Php, Perl, Python, Bash, MySQL, openDirectory.}
\end{itemize}
}

\cventry{January 2007}{Junior-Entreprise Consultant}{MVA Limited}{Grenoble}{}
{
\begin{itemize}
\item[-]{Development of a GPS coordinate extraction tools using Google Maps.}
\item[-]{Environment: \textbf{Java}, Swing}
\end{itemize}
}

\cventry{Octobre 2006}{Junior-Entreprise Consultant}{Institut Laue-Langevin}{Grenoble}{}
{
\begin{itemize}
\item[-]{Porting of an objective-C crystallography demonstration application to Java.}
\item[-]{Environment: Java, Swing, HTML.}
\end{itemize}
}

\cventry{August 2003}{Intern}{Xyalis}{Grenoble}{}
{
\begin{itemize}
\item[-]{Development of \textbf {non-regression tools} for Xyalis complete software suite.}
\item[-]{Environment: Bash, Tcl, Tk.}
\end{itemize}
}

\cventry{July 2001}{Intern}{Xyalis}{Grenoble}{}
{
\begin{itemize}
\item[-]{Development of demonstration scripts for CAO tools.}
\item[-]{GUI integration of several tools.}
\item[-]{Live demonstration at an international micro-electronic exhibition in the USA.(DAC).}
\item[-]{Environment: Tcl, Tk.}
\end{itemize}
}

\section{Education}
\cventry{2010}{Computing Science Engineer}{ENSIMAG}{Grenoble}{}{}
\cventry{2010}{MSc in Embedded systems}{Northumbria University}{Newcastle}{UK}{
\begin{itemize}
\item[]{In parallel of the third year at ENSIMAG.}
\end{itemize}
}

\section{Personal experience}
\cventry{2008 \\upto Today}{Contributions to Open Source projects}{}{}{}
{
\begin{itemize}
\item[-]{Contribution to mailing list and development of \textbf{Linux}, \textbf{Git}, OpenSM.}
\end{itemize}
}

\cventry{2011 \\upto Today}{Damage (DAtabase MetA GEnerator)}{}{}{}
{
\begin{itemize}
\item[-]{Development of a script toolset for custom database generation.}
\item[-]{Generates a complete access and modification API for C, Java, Ruby to XML/YAML/Binary databases from a simple YAML description.}
\item[-]{Environnement: Ruby, GPL}
\end{itemize}
}
\cventry{2006}{Participation to  IBM Cell B.E. Contest}{}{}{}
{
\begin{itemize}
\item[-]{Development of a generic Open Source $producer/consumer$ framework for Cell clusters.}
\item[-]{Environment: C++, sockets}
\end{itemize}
}
\cventry{2005 \\upto 2007}{IT Administrator of N'Sigma, ENSIMAG Junior-Entreprise}{}{}{}
{
\begin{itemize}
\item[-]{Administration of a mixed Linux/Windows network.}
\item[-]{Participation to cost assessments of N'Sigma contracts.}
\end{itemize}
}

\cventry{2005}{Development of a micro-controller}{}{}{}
{
\begin{itemize}
\item[-]{Development and debug of an 8bit micro-controller with VGA output on a FPGA.}
\end{itemize}
}

\cventry{2004}{National programming contest Prologin}{}{}{}
{
\begin{itemize}
\item[]{Development of an AI for a strategy game.}
\item[]{Ranked \textbf{5th}}
\end{itemize}
}

\section{Skills}
\subsection{Computer}
\cvcomputer
{Languages}{\textbf{C}, \textbf{Ruby}, Java, Assembly, Tcl, Ada, Php, C++}
{Development tools}{Emacs, Netbeans, SQLDevelopper, Eclipse}
\cvcomputer
{Operating System}{\textbf{Kernel}, \textbf{Scheduling}, Concurrent programming, \textbf{Drivers}, Signals}
{Version Control}{\textbf{Git}, \textbf{Gitolite}, \textbf{Hudson}, CVS, SVN, SCCS}


\cvcomputer
{Administration}{\textbf{Linux}, FreeBSD, Samba, Postfix, Apache, Shell scripting (Bash, Sed, Awk)}
{Networking}{Routing, Firewall, TCP/IP, Ethernet, \textbf{Sockets}, QoS, \textbf{Infiniband}}

\cvcomputer
{Graphical Environment}{\textbf{X11}, Gtk, Tk, Swing}
{Databases}{\textbf{Conception}, Optimisation, \textbf{SQL}, Oracle, MySQL, LDAP.}

\cvcomputer
{Software Design}{\textbf{UML}}
{Hardware Design}{\textbf{VHDL}, Modelsim}

\cvcomputer
{Mathematic tools}{Matlab, CoinOR, GPLK}{}{}

\subsection{Languages}
\cvlanguage{French}{Native speaker}{}
\cvlanguage{English}{Bilingual}{TOEFL Score: 100/120}
\cvlanguage{German}{School level}{}

\section{Others}
\cvline{Hobbies}{Hiking, skiing, travelling, photography, books and movies.}
\cvline{Sport}{Former hang-glider pilot, member of the French Youth National team.}

\end{document}
